\section{Presentations} 
\hangindent=2em
\hangafter=1
Matthew Moreno. \textit{Evolvability and Plasticity in a Genetic Regulatory Network Model}. Math and Computer Science Department Seminar Series, University of Puget Sound, April 2017. 

\vspace {-3.5 mm}

\hangindent=2em
\hangafter=1
Matthew Moreno. \textit{Modeling the Collective Behavior of Ants on Uneven Terrain}. Phi Sigma Undergraduate Research Symposium, University of Puget Sound, April 2017. 

\vspace {-3.5 mm}

\hangindent=2em
\hangafter=1
Matthew Moreno. \textit{Evolvability: What Is It and How Do We Get It?}. Otis C. Chapman Honors Program Thesis Presentation, University of Puget Sound, March 2017. 

\vspace {-3.5 mm}

\hangindent=2em
\hangafter=1
Matthew Moreno. \textit{Modeling the Collective Behavior of Ants on Uneven Terrain}. Joint Mathematics Meetings, Atlanta, GA. January 2017. 

\vspace {-3.5 mm}
\hangindent=2em
\hangafter=1
Matthew Moreno. \textit{Modeling Ant Foraging on Uneven Terrain}. Elements Science Magazine, University of Puget Sound. December 2016. 

\vspace {-3.5 mm}
\hangindent=2em
\hangafter=1
Matthew Moreno. \textit{Evolvability in Evolving Artificial Neural Networks}. NW Honors Research Symposium, Seattle Pacific University. November 2016. 

\vspace {-3.5 mm}
\hangindent=2em
\hangafter=1
Matthew Moreno. \textit{Modeling the Collective Behavior of Ants on Uneven Terrain}. Fall Poster Symposium, University of Puget Sound. September 2016. 

\vspace {-3.5 mm}
\hangindent=2em
\hangafter=1
Matthew Moreno. \textit{Modeling the Collective Behavior of Ants on Uneven Terrain}. Undergraduate Capstone Conference, Mathematical Biosciences Institute at The Ohio State University. August 2016. 

\vspace {-3.5 mm}
\hangindent=2em
\hangafter=1
Matthew Moreno and Becky Hanscam. \textit{Relieving the Space Jam: Assessment of
a Quick-Response Satellite Mission to Neutralize Debris from Orbital Fragmentation Events}. Math/CS Day, University of Puget Sound. April 2016. 

\vspace {-3.5 mm}
\hangindent=2em
\hangafter=1
Matthew Moreno. \textit{Automated Extraction of Mouse Vocalizations from Noisy
Recordings}. Fall Poster Symposium, University of Puget Sound. September
2015.

\vspace {-3.5 mm}
\hangindent=2em
\hangafter=1
Matthew Moreno. \textit{Mathematical Contest in Modeling: Eradicating Ebola}.
Math/CS Day, University of Puget Sound. May 2015.


 \vspace {-3.5 mm}
