\documentclass[letter]{res}

\setlength{\textheight}{9.5in}
%\usepackage{fontspec}
\usepackage{geometry}
\usepackage{xcolor}
% \usepackage{natbib}
% \usepackage{bibentry}
% \nobibliography*

\usepackage[utf8]{inputenc}
\geometry{
 a4paper,
 total={210mm,297mm},
 left=15mm,
 right=15mm,
 top=15mm,
 bottom=15mm,
 bindingoffset=0mm
 }\usepackage{fontenc}
\usepackage{enumitem}
\setlist{nolistsep}
%\setmainfont[Mapping=tex-text]{Linux Libertine O}


\begin{document}
\name{Matthew Andres Moreno}
\address{\texttt{https://mmore500.github.io}}
\address{541.740.6595, \texttt{mamoreno@pugetsound.edu}} 
\address{4029 Wheelock Student Center}
\address{Tacoma, Washington 98416}



\begin{resume}
\vspace{-2mm}
% \section{Personal Statement}
% My personal statement goes here.

\vspace{-3.5mm}
\section{Education}
{\sl Bachelors of Science} in Mathematics, Computer Science (GPA: 3.95/4.0) \hfill Expected: May 2017\\
{\sl Minor} in Chemistry \\
University of Puget Sound,  Tacoma, WA
  \vspace{-3.5mm}

\section{Relevant Coursework }
  {\sl Mathematics}: Linear Algebra, Ordinary Differential Equations, Partial Differential Equations, Topology, Probability, Mathematical Statistics, Complex Analysis, Abstract Algebra\\
  {\sl Computer Science}: Assembly Language \& Computer Architecture, Programming Paradigms, Introduction to Artificial Intelligence, Software Engineering, Algorithms and Data Structures \\
  {\sl Biological Sciences}: Organic Chemistry I \& II, Cellular Biology, Genetics
\vspace{-3.5mm}

\section{Skills}
  {\sl Programming Languages}: C, Java, OpenCL, Prolog, Haskell, Python \\
  {\sl Miscellaneous}: \LaTeX, Wolfram Mathematica, Matlab, Bash
\vspace{-3.5mm}

\section{Academic Awards} 
 \begin{itemize}
 \item Dean's List (Spring 2014-Present)
 \item Member of Otis C. Chapman Honors Program (2013-Present)
 \item Member Phi Beta Kappa (2016-Present)
 \item Recipient of Great Lakes National Scholarship Program Award (2016-2017)
 \item Recipient of James R. Slater Phi Beta Kappa Award (2016-2017)
 \item Recipient of Puget Sound Association of Phi Beta Kappa Scholarship (2016-2017)
 \item Recipient of Honors Alumni Scholarship (2015-2016, 2016-2017)
 \item Recipient of Thomas and Hilda Jack (2014-2015), Sprenger (2015-2016, 2016-2017), and McKnight Memorial (2016-2017) Scholarships in chemistry 
 \item Recipient of McGill Family (2015-2016), McKnight (2015-2016), and Thomas and Hilda Jack (2016-2017) Scholarships in mathematics 
 \item Recipient of Beta Theta Pi Men of Principle Scholarship (2014-2015)
 \item Recipient of University of Puget Sound Trustee Scholarship (2013-2017)
 \item National AP Scholar (2013)
%  \item Corvallis High School Outstanding Student in French (2013)
 \end{itemize}
\vspace{-3.5mm}

\section{Research Experience}
\textit{Mathematical Biosciences Institute (MBI) Research Experience for Undergraduates} | Newark, NJ \hfill Summer 2016 \newline 
\textit{- Student Researcher} \\
  \vspace{-4.5mm}
 \begin{itemize}
 \item Designed and numerically evaluated an individual-based set of differential equations to model the foraging behavior of ants over uneven terrain, analyzed predictions of the model over various experimental conditions.
  \item Worked with advisors Jason Graham and Simon Garnier in the Swarm Lab at the New Jersey Institute of Technology.
 \item Gave oral and poster presentations at a capstone conference in Columbus, Ohio.
 \item Attended seminars and workshops on mathematical biology coordinated by MBI at The Ohio State University.
 \end{itemize}
  \vspace{-3.5mm}

\textit{Automated Extraction of Mouse Ultrasonic Vocalizations from Noisy Recordings} | Tacoma, WA \hfill Summer 2015 \newline 
\textit{- Student Researcher} \\
  \vspace{-4.5mm}
 \begin{itemize}
 \item Designed, applied for grant funding, and carried out project with advisor Adam Smith.
 \item Funded for eleven weeks as a NASA Research Scholar.
 \item Developed and tested filtering algorithms inspired by the Sobel Edge detection method that, after being trained on human-annotated spectrograms of mouse vocalizations, distinguish between true mouse vocalization signals and background noise.
 \item The project culminated in a poster session on campus attended by faculty, summer research students, and other students. 
 \end{itemize}
  \vspace{-3.5mm}
  
COMAP Mathematical Contest in Modeling | Tacoma, WA \hfill Spring 2015, 2016 \newline 
\textit{- Contest Participant} \\
  \vspace{-4.5mm}
 \begin{itemize}
 \item Collaborated in a small team of three students for four days to develop a mathematical model in response to a prompt.
 \item The project results in a journal-style paper describing our model, results, and outlining reccomendations to policy makers.
 \item In 2015, developed an epidemiological model to investigate the spread of Ebola virus disease and make recommendations on vaccine distribution.
 \item In 2016, developed a model of satellite fragmentation events and the subsequent disbursement of debris in orbit to investigate the feasibility of quick-response efforts to neutralize debris generated by satellite explosions and collisions; our team received received an ``Honorable Mention'' designation in the competition.
 \end{itemize}
  \vspace{-3.5mm}

US Department of Agriculture Horticultural Crops Research Unit | Corvallis, OR  \hfill  June 2013 – Present \newline
\textit{- Biological Science Aide}\\
  \vspace{-4.5mm}
 \begin{itemize}
 \item Collect data for patent applications, perform plant propagation, assist with field maintenance.
 \end{itemize}
  \vspace{-3.5mm}
 
 John Fowler Laboratory at Oregon State University | Corvallis, OR \hfill Summer 2011, 2012 \newline
\textit{- Laboratory Assistant} \\
 \vspace{-4.5mm}
 \begin{itemize}
 \item Performed experimental inquiry into the role of the exocyst complex in \textit{Arabidopsis thaliana} culminating in a symposium presentation.
 \end{itemize}
  \vspace{-3.5mm}
  
\section{Publications and Presentations} 
\hangindent=2em
\hangafter=1
Matthew Moreno. \textit{Evolvability in Evolving Artificial Neural Networks}. Honors Thesis Presentation, University of Puget Sound, March 2017. 

\vspace {-3.5 mm}

\hangindent=2em
\hangafter=1
Matthew Moreno. \textit{Modeling the Collective Behavior of Ants on Uneven Terrain}. Joint Mathematics Meetings, Atlanta, GA, January 2017. 

\vspace {-3.5 mm}
\hangindent=2em
\hangafter=1
Matthew Moreno. \textit{Modeling Ant Foraging on Uneven Terrain}. Elements Science Magazine, University of Puget Sound, December 2016. 

\vspace {-3.5 mm}
\hangindent=2em
\hangafter=1
Matthew Moreno. \textit{Evolvability in Evolving Artificial Neural Networks}. NW Honors Research Symposium, Seattle Pacific University, November 2016. 

\vspace {-3.5 mm}
\hangindent=2em
\hangafter=1
Matthew Moreno. \textit{Modeling the Collective Behavior of Ants on Uneven Terrain}. Fall Poster Symposium, University of Puget Sound, September 2016. 

\vspace {-3.5 mm}
\hangindent=2em
\hangafter=1
Matthew Moreno. \textit{Modeling the Collective Behavior of Ants on Uneven Terrain}. Undergraduate Capstone Conference, Mathematical Biosciences Institute at The Ohio State University, August 2016. 

\vspace {-3.5 mm}
\hangindent=2em
\hangafter=1
Matthew Moreno and Becky Hanscam. \textit{Relieving the Space Jam: Assessment of
a Quick-Response Satellite Mission to Neutralize Debris from Orbital Fragmentation Events}. Math/CS Day, University of Puget Sound, April 2016. 

\vspace {-3.5 mm}
\hangindent=2em
\hangafter=1
Matthew Moreno. \textit{Automated Extraction of Mouse Vocalizations from Noisy
Recordings}. Fall Poster Symposium, University of Puget Sound, September
2015.

\vspace {-3.5 mm}
\hangindent=2em
\hangafter=1
Matthew Moreno. \textit{Mathematical Contest in Modeling: Eradicating Ebola}.
Math/CS Day, University of Puget Sound, May 2015.

\vspace {-3.5 mm}
\hangindent=2em
\hangafter=1
Matthew Moreno. \textit{Screening for NERDs in Arabidopsis thaliana}. Apprenticeships in Science and Engineering Symposium, University of Portland, August 2011.

 \vspace {-3.5 mm}
 
\section{Employment}
University of Puget Sound Center for Writing, Learning, and Teaching \hfill September 2015 – Present \newline 
\textit{ - Tutor and Academic Consultant}  \\
%  \vspace{-4.5mm}
%  \begin{itemize}
%  \item Tutor math students, helping them work through assignments and prepare for tests.
%  \item Liase with faculty members to discuss coursework and best prepare students.
%  \end{itemize}
% \vspace{-3.5mm}
University of Puget Sound Mathematics and Computer Science Department \hfill  September 2014 – Present \newline
\textit{- Tutor and Grader} \\
  \vspace{-4.5mm}
%   \begin{itemize}
%   \item Tutor math students, helping them work through assignments and prepare for tests.
%    \item Grade introduction to computer science homework assignments and provide detailed feedback to students.
%   \end{itemize}
    \vspace{-3.5mm}
    
University of Puget Sound Chemistry Department \hfill September 2013 – May 2016 \newline 
\textit{- Storeroom Assistant} \\
  \vspace{-4.5mm}
%   \begin{itemize}
%   \item Assist with chemical disposal, inventory control, preparation for laboratory sections.
%   \end{itemize}
    \vspace{-3.5mm}


\section{Service Activities}
\begin{itemize}
    \item National Conference on Peer Tutoring in Writing, Session Chair and Volunteer (2016)
  	\item Mount Tahoma High School, tutor (2016)
	\item University of Puget Sound Access Services, access coach for Tuesday Night Tutoring (2016)
    \item Jason Lee Middle School Access to College Days, student panelist (2016)
	\item Oakland High School, Homework Club leader and classroom assistant (2016)
	\item Youth Orchestral Recital Series, ensemble member (2016)
    \item University of Puget Sound Office of Donor Relations, student speaker (2016)
    \item Puget Sound Wind Youth Wind Ensemble, coach (2015-2016)
    \item University of Puget Sound Student Accessibility and Accommodation, note taker (2015, 2016)
    \item University of Puget Sound Commencement Band, performer (2014, 2015, 2016)
    \item University of Puget Sound Wind Ensemble and Symphony tours, performer (2014, 2015, 2016)
    \item Puget Sound Conductors Institute, ensemble member (2014, 2015)
    \item ACM International Collegiate Programming Contest, volunteer (2014, 2015)
    \item Le Comte Ory, pit orchestra player (2015)
    \item Wilson High School, AP Tutor (2014)
    \item Jacobsen Children's Concert, performer (2014)
    \item Collage Concert, performer (2014)

\end{itemize}
\vspace{-3.5mm}
\section{Extracurricular Activities}
\begin{itemize}
	\item Oboe performance in University Wind Ensemble (co-principal) and Symphony, private study
    \item Model United Nations Club, conference delegate and treasurer (2013 - 2016)
    \item University of Puget Sound Economics Department Blog, contributor (2013 - 2016)
\end{itemize}
% \section{Interests \& Activities} 
% \begin{itemize}
% 
% 
% \item Sports including Italian foil fencing, skiing, running
% 
%  \end{itemize}

\end{resume}

\end{document}



